\documentclass[11pt,a4paper]{article}

% -------------------- Packages --------------------
\usepackage[left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{setspace}

% -------------------- Formatting --------------------
\setstretch{1.05}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0em}
  {}
  [\titlerule]

% -------------------- Document --------------------
\begin{document}

\begin{center}
    {\LARGE \textbf{Adarsh Liju Abraham}} \\
    \vspace{4pt}
    \href{mailto:adarsh.liju.abraham@gmail.com}{adarsh.liju.abraham@gmail.com} \;|\;
    +91 8088229177
\end{center}

% -------------------- Education --------------------
\section*{Academic Qualification}
\textbf{Bachelor of Technology in Computer Science Engineering} \\
PES University (PESU) \hfill May 2024

% -------------------- Experience --------------------
\section*{Work Experience}

\textbf{System Engineer — Twospoon Technologies, Bengaluru} \hfill Oct 2024 -- Present
\begin{itemize}
    \item Developed highly scalable Flask-based APIs serving \textbf{100K+ daily requests} for ReactJS frontends.
    \item Architected and implemented microservices, reducing deployment time by \textbf{40\%}.
    \item Designed SNMP-based network monitoring integrated with \textbf{Grafana, Prometheus, and Checkmk}, ensuring \textbf{99.9\% uptime}.
    \item Built automation pipelines that reduced manual operational effort by \textbf{80\%}.
    \item Created reusable deployment scripts and templates, standardizing high-performance rollouts across projects.
    \item Collaborated cross-functionally with frontend and product teams, improving system responsiveness by \textbf{30\%}.
    \item Performed backend performance profiling, reducing API response times by \textbf{200ms+} under peak load.
    \item Authored detailed infrastructure documentation, improving onboarding and incident response efficiency.
    \item Enforced security best practices including API authentication, log auditing, and patch management.
\end{itemize}

\vspace{4pt}

\textbf{Python Engineer — Caliper Business Pvt. Ltd., Bengaluru} \hfill May 2024 -- Oct 2024
\begin{itemize}
    \item Developed and maintained REST APIs using \textbf{Django and Django REST Framework}.
    \item Built scalable Pandas-based services processing \textbf{1M+ records daily}.
    \item Automated complex Excel workflows, reducing manual processing time by \textbf{70\%}.
    \item Optimized backend services, achieving a \textbf{60\% reduction} in API response time.
    \item Scaled existing systems to onboard \textbf{5 new enterprise clients}.
\end{itemize}

% -------------------- Internships --------------------
\section*{Internships}

\textbf{Developer \& Analytics Intern — Caliper Business Pvt. Ltd., Bengaluru} \hfill Feb 2024 -- May 2024
\begin{itemize}
    \item Built backend infrastructure for a planner application using Django, reducing response time by \textbf{40\%}.
    \item Designed a ReactJS frontend improving user engagement by \textbf{25\%}.
    \item Integrated AI-based demand prediction models achieving \textbf{85\% forecast accuracy}.
    \item Worked on demand forecasting and warehouse analytics pipelines.
\end{itemize}

\vspace{4pt}

\textbf{SME Lecturer — PESUIO, Bengaluru} \hfill Jun 2022 -- Sep 2023
\begin{itemize}
    \item Taught Linux fundamentals and command-line tools to \textbf{20+ students} with a \textbf{90\% completion rate}.
    \item Conducted hands-on sessions on shell scripting, kernel modules, and system programming.
    \item Led discussions on FOSS principles and Linux system internals.
\end{itemize}

\vspace{4pt}

\textbf{Research Intern — CHIPS, Bengaluru} \hfill May 2022 -- Jul 2022
\begin{itemize}
    \item Conducted research on \textbf{Manycore RISC-V architectures} for parallel computing optimization.
    \item Benchmarked OpenMP and MPI implementations for performance insights.
\end{itemize}

% -------------------- Projects --------------------
\section*{Academic Projects}

\textbf{Project Turtle} \hfill Team Size: 2
\begin{itemize}
    \item Developed a robust shell script to automate installation of essential Linux tools.
    \item Implemented cross-distro compatibility checks and error handling.
    \item Open-source Hacktoberfest project used to bootstrap Linux servers and workstations.
\end{itemize}

\textbf{Yet Another Markdown Converter} \hfill Team Size: 1
\begin{itemize}
    \item Built a CLI tool to convert Markdown to HTML with customizable themes.
    \item Designed for automation-friendly terminal workflows.
\end{itemize}

\textbf{DoctorPres} \hfill Team Size: 1
\begin{itemize}
    \item Developed a digital prescription system using Streamlit and MySQL.
    \item Implemented triggers and stored procedures for data validation and complex queries.
    \item Used official Indian Government datasets for medicines and diseases.
\end{itemize}

\textbf{Capstone Project (Final Year Project)} \hfill Team Size: 4
\begin{itemize}
    \item Built a secure decentralized DApp platform using blockchain technology.
    \item Implemented an ONOS controller cluster to eliminate single points of failure.
    \item Evaluated performance, scalability, and security of SDN-based architectures.
\end{itemize}

% -------------------- Publications --------------------
\section*{Publications}

\begin{itemize}
    \item \textbf{ONOS SDN Framework: Assessing the Impact of Single and Multi-Controller Architectures on Network Efficiency} \\
    Springer SmartCom 2024
    \item \textbf{Enhancing Disaster Response: A Study on SDN-Integrated Alarm and Alert Systems Using Cooja Simulations} \\
    IEEE NKCON 2023
\end{itemize}

% -------------------- Workshops --------------------
\section*{Workshops}

\begin{itemize}
    \item Conducted a workshop on \textit{Linux, Git, and Open-Source Contribution} — PES University, Jan 2023.
    \item Conducted a \textit{Golang Workshop} — PES University, Feb 2023.
\end{itemize}

% -------------------- Skills --------------------
\section*{Technical Skills}

\begin{itemize}
    \item \textbf{Languages:} Python, JavaScript, C, C++, PHP, Bash, MySQL, Golang (Basics)
    \item \textbf{Systems:} Linux, Docker, Kernel Programming, SQL
    \item \textbf{Frameworks \& Tools:} Django, Flask, ReactJS, Git, AWS, Pandas, OpenMP, MPI, SNMP
    \item \textbf{Foundations:} DBMS, Operating Systems, OOPS, Web Development
\end{itemize}

% -------------------- Extras --------------------
\section*{Extracurricular Activities \& Achievements}

\begin{itemize}
    \item Mentored students through HackerSpace Club, organizing hackathons and guiding innovative projects.
    \item Active participant in FOSS presentations and hackathons.
    \item Led capstone project execution, managing timelines and team collaboration.
\end{itemize}

\end{document}
